Run models

### 2017-01-27 Code/3_validation/run-models.Rmd
model for first 5 non0 states

```{r fit_models_alabama_males}
#run time: 15 minutes
#fit the bayesian models and put the 1000 posterior samples into a data frame
r.White <- run_analysis(dataset = dat.clean, state1 = "Alabama", sex1 = "Male", race1 = "White")
r.White$race <- "White"

r.Black <- run_analysis(dataset = dat.clean, state1 = "Alabama", sex1 = "Male", race1 = "Black")
r.Black$race <- "Black"
```

```{r prepare_data_for_le_functions}
#run time: about 2 minutes
r.All <- rbind(r.White, r.Black)
rm(r.White, r.Black)

@@

r.All <- r.All %>% group_by(post.samp, state, race.sex, year.n, age_minbin) %>%
                           arrange(post.samp, state, race.sex, year.n, age_minbin) %>%
                           mutate(total_smoothed_deaths = sum(smoothed_deaths),
                                  cod_prop_smoothed_deaths = smoothed_deaths/total_smoothed_deaths)
```

```{r run_calculations}
#run time ~40 mins
#run the life table and decomposition calculations for each of the 1000 posterior samples

@@

    print(stratum_i)
    rm(data_sub)
  }
)
rm(counter)

@@

for(i in 1:n) {

@@

  rm(age.cod.decomp.posteriors2)
}
```

>>>>

```{r fit_models_alabama_males}
#run time: expect 2 hours
#fit the bayesian models and put the 1000 posterior samples into a data frame

system.time(
  for(sex_i in c("Male", "Female")){
    for(state_i in c("Alabama", "Arizona", "Arkansas", "California")) {
      assign(paste0("r.White.", state_i, sex_i), run_analysis(dataset = dat.clean, state1 = state_i, sex1 = sex_i, race1 = "White"))
      assign(paste0("r.Black.", state_i, sex_i), run_analysis(dataset = dat.clean, state1 = state_i, sex1 = sex_i, race1 = "Black"))  
    }
  }
)

r.White <- rbind(r.White.Alabama.Male, r.White.Arizona.Male, r.White.Arkansas.Male, r.White.California.Male,
                 r.White.Alabama.Female, r.White.Arizona.Female, r.White.Arkansas.Female, r.White.California.Female)
r.White$race <- "White"

r.Black <- rbind(r.Black.Alabama.Male, r.Black.Arizona.Male, r.Black.Arkansas.Male, r.Black.California.Male,
                 r.Black.Alabama.Female, r.Black.Arizona.Female, r.Black.Arkansas.Female, r.Black.California.Female)
r.Black$race <- "Black"
```

```{r prepare_data_for_le_functions}
#run time: used to be 2 minutes
r.All <- rbind(r.White, r.Black)
rm(r.White, r.Black)

@@

system.time(r.All <- r.All %>% group_by(post.samp, state, race.sex, year.n, age_minbin) %>%
                           arrange(post.samp, state, race.sex, year.n, age_minbin) %>%
                           mutate(total_smoothed_deaths = sum(smoothed_deaths),
                                  cod_prop_smoothed_deaths = smoothed_deaths/total_smoothed_deaths))
```

```{r run_calculations}
#run time ~40 mins -- expect 5.5 hours
#run the life table and decomposition calculations for each of the 1000 posterior samples

@@

    print(stratum_i)
    rm(data_sub)
  }
)

@@

system.time(
  for(i in 1:n) {

@@

    rm(age.cod.decomp.posteriors2)
  }
)
```
